### 2012-11-25 paper.tex

\paragraph{}As further preprocessing for Naive Bayes it is important to dicretize the numerical attributes. The PKIDescretizer was used again as it produces better bin sizes than the standard discretizer without any configuration.

\paragraph{}After the first run with the Simple Naive Bayes algorithm we gain the result shown in table \label{tab:adult:bayes:1d} and a confusion matrix \ref{tab:adult:bayes:1c}.

>>>>

\paragraph{}As further preprocessing for Naive Bayes it is important to dicretize the numerical attributes. The PKIDescretizer was used again as it produces better bin sizes than the standard discretizer without any configuration. After the first run with the Simple Naive Bayes algorithm we gain the result shown in table \ref{tab:adult:bayes:1d} and a confusion matrix \ref{tab:adult:bayes:1c}.
